---
title: "case_study"
runtime: shiny
output: html_document
date: "2024-02-11"
params:
  selected_dataset: 5
  selected_query_type: 2
  query_count_table: NA
  selected_paper_id: 1
---



```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = FALSE)
```

## Query Generation

Below are the query components that were generated for dataset params$selected dataset.

```{r echo=FALSE}


###THIS CHUNK SHOULD PRINT THE LIST OF QUERIES (THEIR ACTUAL TEXT)
```

## Semantic Search
Each of the six queries returned X potentially relevant papers.


```{r echo=FALSE}
# Load required libraries



# Server for Shiny app
# server <- function(input, output) {
#   # Reactive function to read and display results based on user input
#   query_results <- reactive({
#     # Build file path based on user input
#     file_path <- paste0("dataset", input$selected_dataset, "_query", input$selected_query, ".csv")
# 
#     # Load results for the selected dataset and query
#     results <- read.csv(file_path)
# 
#     # Count the number of rows in the results
#     query_count <- nrow(results)
# 
#     # Create a data frame for displaying results
#     query_count_table <- data.frame(query_type = input$selected_query, query_count = query_count)
# 
# 
#   })
# 
#   # Render the table based on reactive function
#   output$query_results <- renderTable({
#     query_results()
#   }, sanitize.text.function = function(x) x)
# }

selectInput(
    inputId = "selected_dataset",
    label = "Select dataset number",
    choices = c(189, 154, 160),
    selected = 189,
    multiple = FALSE,
    selectize = TRUE,
    width = NULL,
    size = NULL
)

selectInput(
    inputId = "selected_query_type",
    label = "Select query type",
    choices = c(1:6),
    selected = 1,
    multiple = FALSE,
    selectize = TRUE,
    width = NULL,
    size = NULL
)

output_table <- reactive({data.frame(select1 = input$selected_dataset
               , select2 = input$selected_query_type)})


renderTable({ 
    output_table()
}) 



# Print the results using kableExtra::kbl
table <-  kableExtra::kbl(
      x = query_count_table,
      valign = "t",
      caption.short = "Number of search results for the selected query",
      full_width = F,
      format = "markdown"
)  %>% kable_styling("striped")


# Return the table
table
 
```

## Topic Modeling

Out of the XX papers returned across the six query types, YYY had abstracts available in either the NLP4Dev or Semantic Scholar corpuses, and ZZZ had full body text available.

These were used as inputs to the NLP4Dev API, as described in Section 3.5.

XXX were defined as relevant.

##my version
```{r echo=FALSE}
library(here)
setwd(here::here())

# Read the first CSV file
csv_path_1 <- here("data", "topic39_summary_abstract_body.csv")
your_csv_data_1 <- read.csv(csv_path_1)

# Read the second CSV file
csv_path_2 <- here("data", "majority_country_summary_abstract_body.csv")
your_csv_data_2 <- read.csv(csv_path_2)

# Read the third CSV file
csv_path_3 <- here("data", "jdc_count_summary_abstract_body.csv")
your_csv_data_3 <- read.csv(csv_path_3)


selectInput(
    inputId = "selected_paper_id",
    label = "Select paper ID",
    choices = unique(your_csv_data_1$paper_id),
    selected = params$selected_paper_id,
    multiple = FALSE,
    selectize = TRUE,
    width = NULL,
    size = NULL
)

# Render output for selected topic
renderUI({
  if (!is.null(params$selected_paper_id)) {
    selected_paper_1 <- your_csv_data_1[your_csv_data_1$paper_id == params$selected_paper_id, ]
    selected_paper_2 <- your_csv_data_2[your_csv_data_2$paper_id == params$selected_paper_id, ]
    selected_paper_3 <- your_csv_data_3[your_csv_data_3$paper_id == params$selected_paper_id, ]
    
    output_data <- data.frame(
      Abstract_Topic39 = selected_paper_1$topic_39_abstract,
      Full_Text_Topic39 = selected_paper_1$topic_39_full_text,
      Abstract_Majority_Country = selected_paper_2$abstract_majority_country,
      Body_Majority_Country = selected_paper_2$body_majority_country,
      Abstract_Tag_count = selected_paper_3$jdc__tag_count_abstract,
      Full_Text_Tag_count = selected_paper_3$jdc__tag_count_full_text
    )
    
    kable_styling("striped") %>% 
      HTML()
  } else {
    "Please select a paper ID."
  }
})



```


##code template below

```{r echo=FALSE}
relevance_summary_table <- data.frame(query_type = c(1:6), total_result_count = NA, full_text_available = NA, abstract_only = NA, relevant = NA)
# Calculate the figures for full text and abstract, and use them to populate the table



table <- kableExtra::kbl(
    x = relevance_summary_table,
    valign = "t",
    caption.short = "Summary of results per query"
, full_width = F
,format = "markdown"
) %>% kable_styling("striped")

table
```


## Model Output

Following manual review of the papers identified automatically, XXX were confirmed as relevant. Of these XXX, YYY had previously been identified through the manual procedure, and ZZZ were new.

This represents a XXX percent improvement over the baseline.
```{r echo=FALSE}
## UPDATE THIS SECTION AFTER THE PREVIOUS SECTION IS COMPLETE
# relevant_result_breakdown <- ggplot(relevance_summary_table)
# Calculate the figures for full text and abstract, and use them to populate the table

# plot(relevant_result_breakdown)
```


## Evaluating Model Performance

Based on our selected evaluation metric, Query X performed most effectively.

```{r echo=FALSE}
top_query <- relevance_summary_table$query_type[which.max(relevance_summary_table$relevant)] 
# Calculate the figures for full text and abstract, and use them to populate the table

table <- kableExtra::kbl(
    x = top_query,
    valign = "t",
    caption.short = "Summary of results per query"
, full_width = F)
 
table
```

## Network

Below is the distribution of fields and geographic locations from the papers that referenced this dataset.

```{r echo=FALSE}
#selectInput("query_type", label = "Select a query type:",
#              choices = c(1:6), selected = 1)

#renderPlot({
#  coverage_heat_map(params$selected_dataset,params$selected_query_type)
#})
```